The Impact of Education <br>

### 2014-12-04 Presentation/EdEntrePres.Rmd
Edited DF for WayofTeaching, added ggplot2 charts

## Different Country-level Perceptions of Good Opportunities to Start a Business

@@

## Distribution of Perception Differences
```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library("ggplot2")

@@

# Edit column names
names(Opp3) <- gsub("value", "WayofTeaching", names(Opp3))
names(Opp3) <- gsub("variable", "Year", names(Opp3))

Opp3$iso2c <- NULL

# Create plot
ggplot(Opp3,aes(x=Year,y=WayofTeaching,colour=Country,group=Country)) + geom_line()

@@

subset
ggplot1
geom_line color each country
colors by country 4-5

## Slide with R Code and Output
```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

## WayofTeaching
```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Import GEM data frame
WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")

@@

@@

Table2 <- gvisTable(WT, 
               options=list(width=230, height=300))

WTT <- gvisMerge(WT_map, Table, horizontal = TRUE)

@@

## Slide with Plot

>>>>

## Varying Perceptions of Good Opportunities to Start a Business in OECD Countries

@@

## Variation in Perceived Opportunities to Start a Business
```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library("ggplot2")
library("reshape2")

@@

# Edit column names
names(Opp3) <- gsub("value", "PerceivedOpportunities", names(Opp3))
names(Opp3) <- gsub("variable", "Year", names(Opp3))

Opp3$iso2c <- NULL
```

```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

# Create plot
ggplot(Opp3,aes(x = Year, y = PerceivedOpportunities, colour = Country, group = Country)) + geom_line()

@@

## Variation in how well Education encourages Self Confidence in OECD Countries

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Import GEM data frame
WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")

@@

# Duplicate df for future use
WT2 <- WT

@@

@@

## Variation in Impact of Education on Self Confidence
```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library("ggplot2")
library("reshape2")

# Import df
Wdf <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv")

# Delete unnessesary columns
Wdf$X <- NULL
Wdf$PercentFear <- NULL
Wdf$PercentNascent <- NULL
Wdf$PercentPerceived <- NULL
Wdf$PercentOwner <- NULL
Wdf$PercentIntention <- NULL
Wdf$PercentOpportunities <- NULL

# Subset WT2
Wdf2 <- subset(Wdf, iso2c %in% myvars2)

```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

# Create plot
ggplot(Wdf2,aes(x = Year, y = WayofTeaching, colour = Country, group = Country)) + geom_line()
